Instructions for *ACL Proceedings

### 2023-07-08 paper/paper.tex
Introdcution and comments

\section{Introduction}
TODO:
\begin{itemize}
  \item how can models reidentify attributes (and objects) from learned encodings in an artificial language \textbf{(done)}
\end{itemize}
Language games with a sender and receiver offer an opportunity on to look at how neural models condense seen information into a distinct representation of symbols. The receiver needs to interpret the meaning of these symbols and combine it with other information. This paper studies how the agents can encode real-looking objects into distinct symbols and decode this message to reidentify this object. Specifically, the study explores discrimination games using an extended version of the CLEVR dataset, focusing on the identification and differentiation of objects based on their attributes such as shape, color, and size.

\section{Background and previous work}

\section{Materials and methods}
TODO:
\begin{itemize}
  \item creation of dataset (CLEVR) \textbf{(done)}
        \begin{itemize}
          \item multiple 'real' objects in scene \textbf{(done)}
          \item 3 attributes (color, size, shape) differentiate objects \textbf{(done)}
          \item using 'dale' setup to uniquely identify target object \textbf{(done)}
          \item extracting bounding boxes \textbf{(done)}
        \end{itemize}
  \item building a language game using EGG \textbf{(done)}
  \item based on feature extractors ResNet \textbf{(done)}
  \item setup of discriminating game of objects in image \textbf{(done)}
  \item message encoder/decoder is auto-encoder
\end{itemize}

\subsection{Dataset}
The dataset used for these experiments is an extended version of the CLEVR dataset \citep{Johnson2016}.\footnote{The extended source code can be found on GitHub: \href{https://github.com/DominikKuenkele/MLT\_Master-Thesis\_clevr-dataset-gen}{https://github.com/DominikKuenkele/MLT\_Master-Thesis\_clevr-dataset-gen}} This dataset includes 3D-generated images depicting scenes with different kinds of objects. Each of these objects has different combinations of attributes, such as \emph{shape}, \emph{color} and \emph{size}. The objects are randomly placed into the scene and assigned with random attributes.
Figure \ref{fig:clevr-extended_example} shows an example of a generated image of this CLEVR dataset. The dataset also contains ground truth information about each image, including attributes and locations for all objects.

\begin{figure}[h]
  \centering
  \includegraphics[width=.8\linewidth]{figures/CLEVR_extended_example.png}
  \caption{Example of a generated image with the extended code}
  \label{fig:clevr-extended_example}
\end{figure}

@@

@@

@@

@@

@@

\end{document}

>>>>

\section{Introduction}
% TODO:
% \begin{itemize}
%   \item how can models reidentify attributes (and objects) from learned encodings in an artificial language \textbf{(done)}
%   \end{itemize}

Agents interact with the physical world through their action and perception and with other agents through language.
Their sensors and actuators (if they are artificial agents but the same also holds for natural agents) allow them to sample the world and their their own state using measures that are continuous in nature such as intensity of light, distance, angles, velocity and others which can be measured with a high degree of accuracy.
On the other hand language that is used to communicta ewith other agents is based on representations that are composed of a limited set of discrete symbols.
How can both domains and representations arising from these interaction be combined? How are ranges of measurements exprseed in a continuous domain mapped to discrete linguistic labels?
How is ambiguity and underpecification resolved?
Ho can agents achive this through interactive grounding \citep{Regier:1996,Roy:2005,Cooper:2023aa}?

% SD 2023-07-08 14:11:44 +0200: A tip for writing LateX on Git: write each sentence in a separate line, this way any edits and conflicts will be much easier to spot and edit that comparing entire paragraphs.

% \section{Background and previous work}

Language games with a sender and a receiver \citep{Clark:1996aa,Bartlett:2005aa,Kirby:2008ab,SteelsLoetzsch:2009,Zaslavsky:2018aa} offer an opportunity to examine how neural models condense seen information into a distinct representation of symbols through linguistic interaction.
A sender describes a perceptual situation that can also be seen by a receiver starting with a random label while
the receiver attempts to interpret the meaning of these symbols and combine it with other information.
It then sends feedback to the sender about its interpretation.
Interaction is optimised based on the communicative success of the sender and the receiver.
Gradually, both agents converge on a set of symbols that they can use to refer to situations in jointly attended perceptual scenes \citep{Chai:2016aa,Kelleher:2020aa}.
Communication is successful and grounding converges because learning is constrained by joint attention and the agents are playing following the rule of the communicative games.

In this this paper we explore how agents based on artificial neural networks learn referential grounding of entitities in images of 3-dimensional scenes where one agent is discribing the entities and the other agent learns to interpret the reference of symbols in the scene either by identifying the object in the scene as a bounding box or location of the object based on object attributes such as shape, colour and size.
% studies how the agents can encode real-looking objects into distinct symbols and decode this message to reidentify this object. Specifically, the study explores discrimination games using an extended version of the CLEVR dataset, focusing on the identification and differentiation of objects based on their attributes such as shape, color, and size.
The novelty of our work compared with the previous work with this setup \citep{Kharitonov2019} is that (i) we extend the popular CLEVR dataset \citep{Johnson2016} with new artificially generated 3-d scenes of objects that that can be referred to and discriminated based on the attributes such as shape, colour and size whereby the discrimination is based on different overalaps of these attributes between the target and the distractor objects; and (ii) we implement a focused referring to objects aither as one of the potential bounding boxes or location of the target.

% SD 2023-07-08 15:05:37 +0200: This hasn't been studied and implemented by lazaridou and others in the EGG framework, right?

% SD 2023-07-08 15:15:46 +0200: Just saw that we are only reporting on object from bounding box identification and not location, right?

% \section{Materials and methods}
% TODO:
% \begin{itemize}
%   \item creation of dataset (CLEVR) \textbf{(done)}
%         \begin{itemize}
%           \item multiple 'real' objects in scene \textbf{(done)}
%           \item 3 attributes (color, size, shape) differentiate objects \textbf{(done)}
%           \item using 'dale' setup to uniquely identify target object \textbf{(done)}
%           \item extracting bounding boxes \textbf{(done)}
%         \end{itemize}
%   \item building a language game using EGG \textbf{(done)}
%   \item based on feature extractors ResNet \textbf{(done)}
%   \item setup of discriminating game of objects in image \textbf{(done)}
%   \item message encoder/decoder is auto-encoder
% \end{itemize}

\section{Our dataset: CLEVR-DaleTwo and DaleFive}

% SD 2023-07-08 14:58:04 +0200: Rephrase this paragraph to continue from the previous section and emphasise our extension and contribution to the dataset. For our experiments we extend...

The dataset used for these experiments is an extended version of the CLEVR dataset \citep{Johnson2016}.\footnote{%The extended source code can be found on GitHub:
  \href{https://github.com/DominikKuenkele/MLT\_Master-Thesis\_clevr-dataset-gen}{https://github.com/DominikKuenkele/MLT\_Master-Thesis\_clevr-dataset-gen}}
This dataset includes 3D-generated images depicting scenes with different kinds of objects. Each of these objects has different combinations of attributes, such as \emph{shape}, \emph{color} and \emph{size}. The objects are randomly placed into the scene and assigned with random attributes.
Figure \ref{fig:clevr-extended_example} shows an example of a generated image of this CLEVR dataset. The dataset also contains ground truth information about each image, including attributes and locations for all objects.

\begin{figure}[h]
  \centering
  \frame{\includegraphics[width=.8\linewidth]{figures/CLEVR_extended_example.png}}
  \caption{Example of a generated image with the extended code} % SD 2023-07-08 15:00:20 +0200: What dataset: Dale-2?
  \label{fig:clevr-extended_example}
\end{figure}

@@

% SD 2023-07-08 15:23:38 +0200: Describe a bit more how DaleTwo and DaleFive differ, in particular how many attributes are shared and how between the objects in the DaleFive?

@@

% SD 2023-07-08 15:09:29 +0200: We have now already said some of this in the introduction. In the introduction we can describe the general setup of language games and here we say explicitly what is our configuration and emphasise in particular in what ways it is different from the previously implemented games. Including a list of technical details of the models is great. When restructuign sentences, copy those that fit the previous section there (and comment one out if necessary) and keep the rest here. It requires a bit of strategic thinking where to mention things in such a short paper so that we only say it once and save space.

@@

% SD 2023-07-08 15:17:45 +0200: The hidden size is related to the vocabulary size. Both have to be optimally selected for the models to converge.

@@

% SD 2023-07-08 15:18:24 +0200: So we are not using just two objects to discriminate with as stated in the introduction and the previous section.

% SD 2023-07-08 15:19:05 +0200: Why is the accuarcy lower? One of the reason of course is that there is more uncertanty and the networks have to learn how different combinations of labels that will be up to n! relate to individual perceptual features that are encoded in the linguistic categories. Since we discrimnate objects based on properties that are also distinguished in human cognition (colour, size, shape) we expect that the vocabulary onto which the agents will converge will reflect these catgories anf therefore be close to human vocabulary. We will imnvestiaget the overlap between the vocabularies in our ongoing and future work.

@@

\end{document}
%%% Local Variables: 
%%% coding: utf-8
%%% mode: latex
%%% mode: flyspell
%%% ispell-local-dictionary: "british"
%%% TeX-engine: default
%%% TeX-master: t
%%% TeX-PDF-mode: t
%%% TeX-command-extra-options: "-shell-escape"
%%% End:
